---
title: "Enron Data Replication"
author: "Olivia Beck"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(igraph)
library(igraphdata)
library(stringr)
library(pscl)
library(LaplacesDemon)
library(stargazer)
library(glmmTMB)
library(dplyr)
library(kableExtra)

set.seed(133458)
```

## Data Set Up

### Node Attributes

```{r}
data(enron)
enron <- upgrade_graph(enron) #see if this is what is causing the discrepancy 

### Attributes
node.att <- vertex.attributes(enron)
edge.att <- edge.attributes(enron)

possible.positions <- c("CEO", "President", "Director", "Manager", "Employee", "Trader", "Lawyer", "NA")

#position is one of the 8 original positions
#need to standardize from the raw data
V(enron)$position <- rep(NA, gorder(enron))
for(i in 1:gorder(enron)){
  #extract language 
  temp <- V(enron)$Note[i]
  temp <- gsub('[[:punct:] ]+',' ',temp)
  temp <- str_split(temp, " ")
  
  #match to possible position
  which.pos <- possible.positions %in% temp[[1]]
  V(enron)$position[i]  <- possible.positions[which.pos]
  
}

#position2 is standardized to CP + DM
V(enron)$position2 <- rep(NA, gorder(enron))
for( i in 1:gorder(enron)){
  temp <- V(enron)$position[i]
  if(temp %in% c("CEO", "President")){V(enron)$position2[i] <- "CP"}
  else if(temp %in% c("Director", "Manager")){V(enron)$position2[i] <- "DM"}
  else(V(enron)$position2[i] <- V(enron)$position[i] )
}

#there should be 77 nodes in total
sum(V(enron)$position2 == 'CP')
sum(V(enron)$position2 == "DM")

sum(V(enron)$position2 == 'CP') + sum(V(enron)$position2 == "DM")
```


### Extract Week 155

```{r}
### Extract week 155 
times <- strptime(E(enron)$Time, format = "%Y-%m-%d")
start155 <-  strptime("2001-10-19", format = "%Y-%m-%d")  #starts 1 second before this time
end155 <- strptime("2001-10-26", format = "%Y-%m-%d") + 24*60*60 -1    #end the last second of the day

keep.edges <- (1:length(E(enron)))[times > start155-1 & times <= end155  ]
range(E(enron)$Time[keep.edges])

enron.week155 <- subgraph.edges(enron, keep.edges, delete.vertices = FALSE)

## Extract CEO/President and Directors/Managers
keep.nodes <- V(enron.week155)[ V(enron.week155)$position2 %in% c("CP", "DM")]
enron77 <- induced_subgraph(enron.week155, keep.nodes)


#getting undirected matrix
enron77.undir <- as.undirected(enron77, mode = "each")
enron77.undir <- simplify(enron77.undir, remove.multiple = FALSE) #remove selfloops

#checking the adjacent matrix is symmetric
mat <- as.matrix(as_adjacency_matrix(enron77.undir))
isSymmetric(as.matrix(mat))

#checking we have the correct number of edges, should be 98
num.pairs.exchange <- sum((mat > 0))/2 
num.pairs.exchange

#converting the multi-edge network to a weighted network
enron77.weighed <- graph.adjacency(mat,
                                   weighted=TRUE,
                                   mode = "undirected")

V(enron77.weighed)$position2 <- V(enron77.undir)$position2


#verify ~ 60% of pairs exchanged more than 5 emails 
#is currntly ~ 48%
mean(E(enron77.weighed)$weight > 5) 

#verify percentage of zero's is 0.966
sum(mat == 0) / nrow(mat)^2

#verify modularity ~0.05
modularity(enron77.weighed, 
           ifelse(V(enron77.weighed)$position2 == "DM",1,2),
           weights = E(enron77.weighed)$weight)

## By hand
Q <- 0
n <- gorder(enron77.weighed)
adj.mat <- as.matrix(as_adj(enron77.weighed, attr = "weight"))
m <- sum(adj.mat/2)
deg <- colSums(adj.mat)
position <- V(enron77.weighed)$position2

for(i in 1:n){
  for(j in 1:n){
    Q <- Q + (adj.mat[i,j] - deg[i]*deg[j]/2/m) * (position[i] == position[j])
  }
}

Q / 2 / m

```



## Fitting the Model

### Set up the Design matrix

```{r}
## Set up D, the design matrix
#initialize
design.mat <- as.data.frame(t(combn(1:77, 2)))
n <- nrow(design.mat)

#Filling out the other variables
design.mat$Val <- design.mat$DMDM <- design.mat$CPCP <- design.mat$CPDM <- rep(NA, n)

for(i in 1:n){
  #value
  design.mat$Val[i] <- mat[design.mat$V1[i], design.mat$V2[i]]
  
  #attributes
  v1.att <- V(enron77.undir)$position2[design.mat$V1[i]]
  v2.att <- V(enron77.undir)$position2[design.mat$V2[i]]
  
  #original attributes 
  design.mat$CPCP[i] <- as.numeric(v1.att == "CP" & v2.att == "CP")
  design.mat$DMDM[i] <- as.numeric(v1.att == "DM" & v2.att == "DM")
  design.mat$CPDM[i] <- as.numeric(v1.att != v2.att)
  
}

```

### Regular Poisson Regression 

Author's Poisson regression estimated model is: 

$$\log(\lambda_{ij}) = -0.74 -0.607*CPDM_{ij} - 0.6 * DMDM_{ij}$$

My estimated model is: 

$$\log(\lambda_{ij}) = -0.719 -0.917*CPDM_{ij} -1.187 * DMDM_{ij}$$
I atleast have the same signs, but I do not have the same parameter estimates. 

```{r}

## Get my model
mod1 <- glm(Val ~ CPDM + DMDM, family="poisson", data = design.mat)
summary(mod1)

design.mat$predicted <- predict.glm(mod1, type = "response")


### Add their model values 
design.mat$their.predicted <- exp(-0.74 -0.607*design.mat$CPDM - 0.6 * design.mat$DMDM)
my.test <- -0.71912 -0.91771*design.mat$CPDM - 1.18705 * design.mat$DMDM


### Table of True y's vs. Predicted y's
table(design.mat$predicted, design.mat$Val)


## My results are predicting all 0's 
table((design.mat$predicted))
plot(design.mat$Val, design.mat$predicted,
     xlab = "true value",
     ylab = "predicted value")

## Their results predict 73% 0
table(design.mat$their.predicted)


### I can get tp 73% by adding the number of obs with the lowest 2 predicted values, 
### But 0.477 is still not rounded to 1 so idk why they claim 73% 0's
(666+1480) /nrow(design.mat) 


```



### ZIP Lapace approx

```{r}

#### Zero inflated poisson regression -------------------------------------
#original model 
mod2 <- zeroinfl(Val ~ 0+ CPCP +CPDM + DMDM | 1, data = design.mat) #original model 


# mod2 <- zeroinfl(Val ~ CPDM + DMDM, data = design.mat) #original model 


summary(mod2) #same as above, very close to theirs but not exact same estimates, standard errors are very close though which makes me hopeful

s.mod2 <- summary(mod2)
s.mod2$coefficients

#stargazer(s.mod2$coefficients)



```



### Mean values 

```{r}
mean0 <- mean(design.mat$Val == 0)
meanCPCP <- design.mat %>% filter(CPCP == 1 & Val > 0) %>% pull(Val) %>% mean()
meanCPDM <- design.mat %>% filter(CPDM == 1 & Val > 0) %>% pull(Val) %>% mean()
meanDMDM <- design.mat %>% filter(DMDM == 1 & Val > 0) %>% pull(Val) %>% mean()


# Model estimate Zeros
invlogit(3.427144)

#approximate estimate zeros
mean0

# Model estimate counts 
coeffs <- s.mod2$coefficients$count[, 1]
exp(c( coeffs[1:3] ))
c(meanCPCP, meanCPDM, meanDMDM)

```


### Likelihood maximize with optim - should be same as pscl package

```{r}
estimate_params <- function(y_A, y_B, y_C, m0, m0_A, m0_B, m0_C) {
  # Sample sizes and means for non-zero responses
  m1_A <- length(y_A)
  m1_B <- length(y_B)
  m1_C <- length(y_C)
  
  m1 <- m1_A + m1_B + m1_C
  
  ybar_A <- mean(y_A)
  ybar_B <- mean(y_B)
  ybar_C <- mean(y_C)
  
  # Negative log-likelihood function
  neg_log_likelihood <- function(params) {
    theta <- params[1]
    lambda_A <- params[2]
    lambda_B <- params[3]
    lambda_C <- params[4]
    
    if (theta <= 0 || theta >= 1 || lambda_A <= 0 || lambda_B <= 0 || lambda_C <= 0) {
      return(Inf)
    }
    
    # Log-likelihood components
    ll_theta <- -m1 / (1 - theta) + m0 / theta - 
      (1 / theta^2) * (m0_A * exp(-lambda_A) + m0_B * exp(-lambda_B) + m0_C * exp(-lambda_C))
    
    ll_lambda_A <- -m1_A + (m1_A * ybar_A) / lambda_A + 
      m0_A * ((1 - theta) / theta) * lambda_A * exp(-lambda_A)
    
    ll_lambda_B <- -m1_B + (m1_B * ybar_B) / lambda_B + 
      m0_B * ((1 - theta) / theta) * lambda_B * exp(-lambda_B)
    
    ll_lambda_C <- -m1_C + (m1_C * ybar_C) / lambda_C + 
      m0_C * ((1 - theta) / theta) * lambda_C * exp(-lambda_C)
    
    # Total negative log-likelihood (sum of squared score functions)
    nll <- ll_theta^2 + ll_lambda_A^2 + ll_lambda_B^2 + ll_lambda_C^2
    return(nll)
  }
  
  # Initial parameter guesses: theta, lambda_A, lambda_B, lambda_C
  init <- c(0.5, mean(y_A), mean(y_B), mean(y_C))
  
  result <- optim(
    par = init,
    fn = neg_log_likelihood,
    method = "L-BFGS-B",
    lower = c(1e-5, 1e-5, 1e-5, 1e-5),
    upper = c(1 - 1e-5, Inf, Inf, Inf)
  )
  
  return(result$par)  # returns estimated theta, lambda_A, lambda_B, lambda_C
}


# Sample non-zero y values
y_A <- design.mat$Val[design.mat$Val > 0 & design.mat$CPCP == 1]
y_B <- design.mat$Val[design.mat$Val > 0 & design.mat$DMDM == 1]
y_C <- design.mat$Val[design.mat$Val > 0 & design.mat$CPDM == 1]

# Known m0 values
m0 <- sum(design.mat$Val == 0 )
m0_A <- sum(design.mat$Val == 0 & design.mat$CPCP == 1)
m0_B <- sum(design.mat$Val == 0 & design.mat$DMDM == 1)
m0_C <- sum(design.mat$Val == 0 & design.mat$CPDM == 1)

optim.results <- estimate_params(y_A, y_B, y_C, m0, m0_A, m0_B, m0_C)

optim.results

#model results 
c(invlogit(3.427), exp(c(coeffs[1], coeffs[1] + coeffs[2], coeffs[1] + coeffs[3]))
)
```


### glmmTMB

```{r}

mod3 <- glmmTMB(Val ~ 0 + CPCP + CPDM + DMDM,
                ziformula =~ 1,
                family =poisson(),
                data = design.mat)

sum3 <- summary(mod3)
coeffs3 <- sum3$coefficients$cond[,1]

exp(c(coeffs3[1:3]))

exp(c(coeffs[1:3]))


```



### Table of Estimates 

```{r}
## Means in betas ( and sd betas)
m <- nrow(design.mat)

# Analytic 
beta.analytic <- c(logit(mean0), log(meanCPCP), log(meanCPDM), log(meanDMDM))

# need delta method for sd estiamtes 
beta0_se <- function(theta, se ){
  return(se / theta / (1-theta))
}


lambda_se <- function(lambda, se){
  return(se / lambda)
}


mCPCP <- sum(design.mat$CPCP == 1 & design.mat$Val > 0)
mCPDM <- sum(design.mat$CPDM == 1 & design.mat$Val > 0)
mDMDM <- sum(design.mat$DMDM == 1 & design.mat$Val > 0)


sd.analytic <- c(beta0_se(mean0 , sqrt(mean0*(1-mean0)/m)), 
                 lambda_se(meanCPCP, sqrt(meanCPCP/mCPCP)),
                 lambda_se(meanCPDM, sqrt(meanCPCP/mCPDM)),
                 lambda_se(meanDMDM, sqrt(meanCPCP/mDMDM)))

## laplace 
coeff.laplace <- coefficients(sum3)

beta.laplace <- c(coeff.laplace$zi[1,1],
                  coeff.laplace$cond[1:3,1])

sd.laplace <- c(coeff.laplace$zi[1,2],
                  coeff.laplace$cond[1:3,2])



coeff.optim <- coefficients(s.mod2)

beta.optim <- c(coeff.optim$zero[1,1],
                  coeff.optim$count[1:3,1])
sd.optim <- c(coeff.optim$zero[1,2],
                  coeff.optim$count[1:3,2])


est.tab <- 
  data.frame(params = c("beta0", "betaCPCP", "betaCPDM", "betaDMDM", "sebeta0", "sebetaCPCP", "sebetaCPDM", "sebetaDMDM"),
             analytic = c(beta.analytic, sd.analytic), 
             laplace = c(beta.laplace, sd.laplace),
             optim = c(beta.optim, sd.optim)) %>% 
  pivot_longer(!params, names_to = "method", values_to = "est")%>% 
  mutate(est = round(est, 6)) %>%
  pivot_wider(names_from = params, values_from = "est") 
  


est.tab

### max means 
max12 <- max(abs(est.tab[1, 2:5] - est.tab[2, 2:5]))
max13 <- max(abs(est.tab[1, 2:5] - est.tab[3, 2:5]))
max23 <- max(abs(est.tab[2, 2:5] - est.tab[3, 2:5]))
max(c(max12, max23, max13))

## max sd 
maxsd12 <- max(abs(est.tab[1, 6:9] - est.tab[2, 6:9]))
maxsd13 <- max(abs(est.tab[1, 6:9] - est.tab[3, 6:9]))
maxsd23 <- max(abs(est.tab[2, 6:9] - est.tab[3, 6:9]))
max(c(maxsd12, maxsd13, maxsd23))
```


## Simulation Study 

```{r}
#### Simulation Study ------------------------------------------------------

# "True" Values 
# Mine
beta0 <- beta.analytic[1]
betaCPCP <- beta.analytic[2]
betaCPDM <-beta.analytic[3]
betaDMDM <- beta.analytic[4]

# ## Theirs
# beta0 <- 2.17
# betaCPDM <- 0.016
# betaDMDM <- 0.40
# gamma0 <- 3.36
# 
theta <- invlogit(beta0)


# Setting up CPDM and DMDM values for every (i,j)
CPCP.mat<- matrix(0, nrow = 77, ncol = 77)
CPDM.mat <- matrix(0, nrow = 77, ncol = 77)
DMDM.mat <- matrix(0, nrow = 77, ncol = 77)
for(i in 1:76){
  for(j in (i+1):77){
    v1.att <- V(enron77.undir)$position2[i]
    v2.att <- V(enron77.undir)$position2[j]
    CPCP.mat[i, j] <- as.numeric(v1.att == "CP" & v2.att == "CP")
    DMDM.mat[i, j] <- as.numeric(v1.att == "DM" & v2.att == "DM")
    CPDM.mat[i, j] <- as.numeric(v1.att != v2.att)
  }
}
CPCP.mat <- CPCP.mat + t(CPCP.mat)
CPDM.mat <- CPDM.mat + t(CPDM.mat)
DMDM.mat <- DMDM.mat + t(DMDM.mat)


# Running the simulation 
N <- 10000
rep <- array(0, c(77, 77, N) )

for(n in 1:N){
  for(i in 1:76){
    for(j in (i+1):77){
      is.from.zero <- rbinom(1, 1, theta)
      if(is.from.zero == 1){rep[i,j,n] <- 0}else{
        current.CPCP <- CPCP.mat[i, j]
        current.CPDM <- CPDM.mat[i, j]
        current.DMDM <-DMDM.mat[i, j]
        l <- exp(betaCPCP*current.CPCP + betaCPDM*current.CPDM + betaDMDM*current.DMDM)
        rep[i,j,n] <- rpois(1, l)
      } #end if else
    }# end j for
  } # end i for
  rep[ , , n] <- rep[ , , n] + t(rep[ , , n ])
} # end n for



## Simulation Parameters 
betaCPCP.sim <- rep(NA, N)
betaCPDM.sim <- rep(NA, N)
betaDMDM.sim <- rep(NA, N)
beta0.sim <- rep(NA, N)

## Centrality Storage 
degree.sim <- matrix(NA, ncol = N, nrow = 77)
strength.sim <- matrix(NA, ncol = N, nrow = 77)
eigen.sim <- matrix(NA, ncol = N, nrow = 77)
between.sim <- matrix(NA, ncol = N, nrow = 77)


#get the design matrix for each iteration
design.temp <- design.mat[, c("V1", "V2", "CPCP", "CPDM", "DMDM")]
design.temp$Val <- rep(NA, nrow(design.temp))

for(n in 1:N){
  A <- rep[ , , n]
  #get the simulated values
  for(i in 1:nrow(design.temp)){
    design.temp$Val[i] <- A[design.temp$V1[i], design.temp$V2[i]]
  }
  # ### Model estimates
  # #get model
  # mod.temp <- zeroinfl(Val ~ 0+CPCP +CPDM + DMDM | 1, data = design.temp)
  # ests.temp <- mod.temp$coefficients
  
  #Store estimates
  beta0.sim[n] <- logit(mean(design.temp$Val ==0))
  betaCPCP.sim[n] <- log(mean(design.temp$Val[design.temp$CPCP == 1 & design.temp$Val > 0]))
  betaDMDM.sim[n] <- log(mean(design.temp$Val[design.temp$DMDM == 1 & design.temp$Val > 0]))
  betaCPDM.sim[n] <- log(mean(design.temp$Val[design.temp$CPDM == 1 & design.temp$Val > 0]))

  ### Centrality estimates
  #get igraph
  # g.temp <- graph_from_adjacency_matrix(A, mode = "undirected", weighted = TRUE)
  
  #get centrality measures
  # degree.sim[ , n] <- igraph::degree(g.temp)
  # strength.sim[ , n] <- igraph::strength(g.temp)
  # eigen.sim[ , n] <- igraph::eigen_centrality(g.temp)$vector
  # between.sim[ , n] <- igraph::betweenness(g.temp, normalized = TRUE)
}




```


### Plot Simulation Results 

```{r}
### Plot Simulation results -------------------------------------------
par(mfrow = c(2,2))
## Parameter Estimates
b=40
ymax =1200

hist(beta0.sim, main = "beta0 simulation",
     ylim = c(0, ymax), 
     breaks=b)
abline(v = beta0, col = "red")


hist(betaCPCP.sim, main = "betaCPCP simulation",
     ylim = c(0, ymax), 
     breaks=b)
abline(v = betaCPCP, col = "red")

hist(betaCPDM.sim, main = "betaCPDM simulation",
     ylim = c(0, ymax), 
     breaks=b)
abline(v = betaCPDM, col = "red")

hist(betaDMDM.sim, main = "betaDMDM simulation",
     ylim = c(0, ymax), 
     breaks=b)
abline(v = betaDMDM, col = "red")
```




```{r}

#table of estimate Results 
df1 <- data.frame(param = c("beta0","betaCPCP", "betaCPDM", "betaDMDM"),
           truevalue = c(beta0, betaCPCP, betaCPDM, betaDMDM), 
           est = c(mean(beta0.sim), mean(betaCPCP.sim), mean(betaCPDM.sim), mean(betaDMDM.sim)),
           sd =  c(sd(beta0.sim), sd(betaCPCP.sim),sd(betaCPDM.sim), sd(betaDMDM.sim)))  
stargazer(df1)


par(mfrow = c(1,1))


## Plot centrality results ---------------------------------
library(ggplot2)
library(dplyr)
##  Degree - Figure 2(a)


degree.frame <- as.data.frame(expand.grid(1:N, 0:max(degree.sim)))
colnames(degree.frame) <- c("samp.number", "degree.value")
degree.frame$prop.degree.value <- NA


for(i in 1:nrow(degree.frame)){
  #get the degrees
  degree.temp <- degree.sim[, degree.frame$samp.number[i]]
  
  #get the number of times that degree occurred in that sample
  count <- (sum(degree.temp == degree.frame$degree.value[i]) )
  
  # get prob of that degree value occurring 
  degree.frame$prop.degree.value[i] <- count / 77
  
  
}


#add on max(degree.sim) + 1 to 25 for plot 
degree.frame2 <- as.data.frame(expand.grid(1:N, (max(degree.sim)+1):25))
colnames(degree.frame2) <- c("samp.number", "degree.value")
degree.frame2$prop.degree.value <- 0

degree.frame <- rbind(degree.frame, degree.frame2)                              


degree.true <- data.frame(degree.value = 0:25, 
                          prop.degree.value = 0)

for(i in 1:nrow(degree.true)){
  degree.true$prop.degree.value[i] <-  sum(igraph::degree(enron77.undir) == degree.true$degree.value[i]) / 77
}

#plot
level_order <- as.character(0:25) 
degree.true$degree.value <- base::factor(degree.true$degree.value, levels = level_order)

degree.frame %>%
  ggplot(aes(x = factor(degree.value, level = level_order), 
             y = prop.degree.value )) +
  geom_boxplot() + 
  geom_point(data = degree.true[1:26, ], 
             aes(x =factor(degree.value, level = level_order), 
                 y = prop.degree.value ), color= "red") +
  xlab('Degree') + 
  ylab("Proportion with degree value in each simulation") +
  ggtitle("Simulation Results of Degree") +
  theme_minimal()

 

## Strength - Figure 2(b)

strength.frame <- as.data.frame(expand.grid(1:N, c(0:10)*30  ))
colnames(strength.frame) <- c("samp.number", "strength.minimum")
strength.frame$strength.maximum <- strength.frame$strength.minimum+30
strength.frame$prop.strength <- NA

for(i in 1:nrow(strength.frame)){
  #get the degrees
  strength.temp <- strength.sim[, strength.frame$samp.number[i]]
  
  #get the number of times that strenth categorty occurred in that sample
  if(strength.frame$strength.minimum[i] == 0){
    count <-  sum((strength.temp >= strength.frame$strength.minimum[i]) & (strength.temp <=strength.frame$strength.maximum[i] ))
  }else{
    count <-  sum((strength.temp > strength.frame$strength.minimum[i]) & (strength.temp <=strength.frame$strength.maximum[i] ))
  }

  # get prob of that strength value occurring 
  strength.frame$prop.strength[i] <- count / 77
  
  
}


strength.true <- data.frame(strength.min = c(0:10)*30, 
                            strength.max = c(0:10)*30 +30,
                            prop.strength = 0)
strength.vals <- strength(enron77.undir)

for(i in 1:nrow(strength.true)){
  count <- sum(strength.vals > strength.true$strength.min[i] & strength.vals <= strength.true$strength.max[i])
  if(strength.true$strength.min[i] ==0){
    count <- count + sum(strength.vals == 0)
  }
  strength.true$prop.strength[i] <- count / 77
}



strength.frame %>%
  ggplot(aes(x = factor(strength.minimum), 
             y = prop.strength )) +
  geom_boxplot() + 
  geom_point(data = strength.true, 
             aes(x =factor(strength.min), 
                 y = prop.strength ), color= "red") +
  xlab('Strength') + 
  ylab("Proportion with Strength range in each simulation") +
  ggtitle("Simulation Results of Strength")+
  scale_x_discrete(labels = c("[0, 30]", "(30, 60]", "(60, 90]",
                              "(90, 120]", "(120, 150]", "(150, 180]",
                              "(180, 210]", "(210, 240]", "(240, 270]",
                              "(270, 300]", "(300, 330]")) +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=45, hjust=1)) 



## Eigenvector - Figure 2(c)

eigen.frame <- as.data.frame(expand.grid(1:N, c(0:9)/10  ))
colnames(eigen.frame) <- c("samp.number", "eigen.minimum")
eigen.frame$eigen.maximum <- eigen.frame$eigen.minimum+0.1
eigen.frame$prop.eigen <- NA

for(i in 1:nrow(eigen.frame)){
  #get the degrees
  eigen.temp <- eigen.sim[, eigen.frame$samp.number[i]]
  
  #get the number of times that strenth categorty occurred in that sample
  if(eigen.frame$eigen.minimum[i] == 0){
    count <-  sum((eigen.temp >= eigen.frame$eigen.minimum[i]) & (eigen.temp <=eigen.frame$eigen.maximum[i] ))
  }else{
    count <-  sum((eigen.temp > eigen.frame$eigen.minimum[i]) & (eigen.temp <=eigen.frame$eigen.maximum[i] ))
  }
  
  # get prob of that eigen value occurring 
  eigen.frame$prop.eigen[i] <- count / 77

}


eigen.true <- data.frame(eigen.min = c(0:9)*.1, 
                            eigen.max = c(0:9)*.1 +.1,
                            prop.eigen = 0)
eigen.vals <- eigen_centrality(enron77.undir)$vector

for(i in 1:nrow(eigen.true)){
  count <- sum(eigen.vals > eigen.true$eigen.min[i] & eigen.vals <= eigen.true$eigen.max[i])
  if(eigen.true$eigen.min[i] ==0){
    count <- count + sum(eigen.vals == 0)
  }
  eigen.true$prop.eigen[i] <- count / 77
}

#Plot
eigen.frame %>%
  ggplot(aes(x = factor(eigen.minimum), 
             y = prop.eigen )) +
  geom_boxplot() + 
  geom_point(data = eigen.true, 
             aes(x =factor(eigen.min), 
                 y = prop.eigen ), color= "red") +
  xlab('Eigenvector Centrality') + 
  ylab("Proportion with eigenvector range in each simulation") +
  ggtitle("Simulation Results of Eigenvector")+
  scale_x_discrete(labels = c("[0.0, 0.1]", "(0.1, 0.2]", "(0.2, 0.3]",
                              "(0.3, 0.4]", "(0.4, 0.5]", "(0.5, 0.6]",
                              "(0.6, 0.7]", "(0.7, 0.8]", "(0.8, 0.9]",
                              "(0.9, 0.10]")) +
  theme_minimal()+
  theme(axis.text.x=element_text(angle=45, hjust=1))



## Betweenness - Figure 2(d)

between.frame <- as.data.frame(expand.grid(1:N, seq(from = 0, to = 0.36, by = 0.04)  ))
colnames(between.frame) <- c("samp.number", "between.minimum")
between.frame$between.maximum <- between.frame$between.minimum+.04
between.frame$prop.between <- NA

for(i in 1:nrow(between.frame)){
  #get the degrees
  between.temp <- between.sim[, between.frame$samp.number[i]]
  
  #get the number of times that strenth categorty occurred in that sample
  if(between.frame$between.minimum[i] == 0){
    count <-  sum((between.temp >= between.frame$between.minimum[i]) & (between.temp <=between.frame$between.maximum[i] ))
  }else{
    count <-  sum((between.temp > between.frame$between.minimum[i]) & (between.temp <=between.frame$between.maximum[i] ))
  }
  
  # get prob of that between value occurring 
  between.frame$prop.between[i] <- count / 77
  
  
}


between.true <- data.frame(between.min = seq(from = 0, to = 0.36, by = 0.04), 
                            between.max = seq(from = 0, to = 0.36, by = 0.04) + 0.4,
                            prop.between = 0)
between.vals <- igraph::betweenness(enron77.undir, normalized = TRUE)

for(i in 1:nrow(between.true)){
  count <- sum(between.vals > between.true$between.min[i] & between.vals <= between.true$between.max[i])
  if(between.true$between.min[i] ==0){
    count <- count + sum(between.vals == 0)
  }
  between.true$prop.between[i] <- count / 77
}



between.frame %>%
  ggplot(aes(x = factor(between.minimum), 
             y = prop.between )) +
  geom_boxplot() + 
  geom_point(data = between.true, 
             aes(x =factor(between.min), 
                 y = prop.between ), color= "red") +
  xlab('Betweenness') + 
  ylab("Proportion with betweenness range in each simulation") +
  ggtitle("Simulation Results of Betweenness") +
  scale_x_discrete(labels = c("[0.0, 0.04]", "(0.04, 0.08]", "(0.08, 0.12]",
                              "(0.12, 0.16]", "(0.16, 0.20]", "(0.20, 0.24]",
                              "(0.24, 0.28]", "(0.28, 0.32]", "(0.32, 0.36]",
                              "(0.36, 0.40]")) +
  theme_minimal()+
  theme(axis.text.x=element_text(angle=45, hjust=1))

```




